Verification of the CVM algorithm with a New Recursive Analysis Technique

### 2025-01-25 isabelle/CVM_Subsample/document/root.tex
Merge Utils_Basic/PMF.   + Minor improvments.
Update root.tex
some very minor edits (minus appendix)

\title{Verification of the CVM algorithm with a new Recursive Analysis Technique}
\author{Emin Karayel, Derek Khu, Kuldeep S. Meel, Yong Kiam Tan,\\and Joe Watt}
\maketitle

@@

In this entry, we verify the CVM algorithm's correctness using a new technique which simplifies
the formal analysis considerably compared to the orignal proof by Chakraborty et
al. The main idea is based on a probabilistic invariant that allows us to derive concentration bounds
using the Cram\'{e}r-Chernoff method.

>>>>

\title{Verification of the CVM algorithm with a New Recursive Analysis Technique}
\author{Emin Karayel, Derek Khu, Kuldeep S. Meel, Yong Kiam Tan,\\and Joe Watt}
\maketitle

@@

In this entry, we verify the CVM algorithm's correctness using a new technique which simplifies
the formal analysis considerably compared to the orignal proof by Chakraborty et
al. The main idea is based on a probabilistic invariant that allows us to derive concentration bounds
using the Cram\'{e}r--Chernoff method.
